The \dealii Library, Version 9.6

### 2024-09-24 9.6/paper.tex
Minor edits.

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
   \item The \texttt{FE\_NedelecSZ} class that contains our 
    implementation of the N\'ed\'elec element using the orientation 
    scheme of \cite{Zag06} now supports the computation of hanging 
    node constraints for locally refined \todo[inline]{hexahedral?} meshes. 
    Therefore, the sign-conflict that arises for hp quadrilateral and 
    hexahedral N\'ed\'elec elements in the presence of hanging edges 
    and hanging faces was addressed for the implementation details; 
    we refer to \cite{Kinnewig2024}. 
    The \texttt{FE\_NedelecSZ} class and the hanging node constraints 
    automatically account for the presence of hanging edges and hanging 
    faces; therefore, there is no difference for the user when using 
    \texttt{FE\_NedelecSZ} as finite elements compared to other finite 
    element classes when used on triangulations with hanging nodes. 
    Note that the special case where, in 3D, more than four cells with 
    different refinement levels share a common edge is not covered yet.
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.

@@

\item Furthermore, we improved the internal data structures of the tensor-product
  evaluators as well as the evaluators for simplex elements.  This speeds up
  the operator evaluation in several scenarios, especially for simplices
  (around two times higher throughput for operator evaluation) and
  multi-component systems. The restructuring made to enable these optimizations
  also reduces the compile times and the size of the generated code slightly.

@@

%\todo[inline]{All: If you contributed to this functionality, please
%  help flesh out this section.}

@@

\item The \texttt{FECouplingValues} class provides a powerful tool for
 integrating finite element data between two different objects, even if they
 live on separate grids or have different topological dimensions (e.g., cells,
 faces, edges). This is particularly useful in the following scenarios: 
 \begin{itemize}
  \item Non-local Differential Operators: Evaluating fractional laplacian or
  boundary element methods.  
  \item Non-matching Discretizations: Integrating data between two independent
  discretization schemes that overlap on some areas. 
  \item Bulk-surface Coupling: Combining data from a bulk discretization and
  surface discretization.
 \end{itemize}

This class enables the combination of degrees of freedom indices, shape
functions, and quadrature points from two existing \texttt{FEValuesBase}
objects. The way this combination is performed is controlled by user-provided
\texttt{DoFCouplingType} and \texttt{QuadratureCouplingType} objects, which
define how the degrees of freedom and quadrature points are combined.

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
  \item \dealii{} now requires and makes use of the C++17 language standard.
  \item We have continued to make progress in supporting simplex and
    mixed meshes -- mesh types that \dealii{} has traditionally not
    supported at all. Specifically, the current release uses
    better strategies for refinement of tetrahedra that result in
    better-shaped child cells. It also contains
    support for cubic finite elements on simplices.
   \item The \texttt{FE\_NedelecSZ} class that contains our 
    implementation of the N\'ed\'elec element using the orientation 
    scheme of \cite{Zag06} now supports the computation of hanging 
    node constraints for locally refined, hexahedral meshes. 
    That is, the implementation of hanging node constraints now
    correctly addresses the sign-conflict that arises for $hp$ quadrilateral and 
    hexahedral N\'ed\'elec elements; 
    see \cite{Kinnewig2024} for details. 
    The other implementation of N\'ed\'elec elements, in the \texttt{FE\_NedelecSZ} class, already
    implements hanging node constraints; therefore, there is no longer
    a difference for the user between the two classes as far as
    constraints are concerned. 
    However, the special case where, in 3D, more than four cells with 
    different refinement levels share a common edge is not covered yet.
  \item The \texttt{AffineConstraints} class stores and processes
    constraints on degrees of freedom in \dealii{}. Such constraints
    can be of the (homogeneous) form $x_3 = \frac 12 x_{14} + \frac 12 x_{15}$ as is
    common when using hanging node constraints (here, $x_3$ could
    represent the value of the solution at a hanging node, and $x_{14}$
    and $x_{15}$ are the values of the two adjacent degrees of freedom on
    the parent edge that contains the hanging node); or they can be of
    the (inhomogeneous) form $x_{12}=42$ as is common when using Dirichlet boundary
    conditions.

@@

\item Furthermore, we improved the internal data structures of the tensor-product
  evaluators as well as the evaluators for simplex elements.  This speeds up
  the operator evaluation in several scenarios, especially for simplices
  (around two times higher throughput for operator evaluation) and
  multi-component systems. The restructuring that led to these optimizations
  also reduced the compile times and the size of the generated code slightly.

@@

@@

\item The \texttt{FECouplingValues} class provides a powerful tool for
 computing
 integrals of functions that contain finite element fields defined on
 different objects, for example if these fields
 live on separate grids or have different topological dimensions (e.g., cells,
 faces, edges). This is particularly useful in the following scenarios: 
 \begin{itemize}
  \item Non-local differential operators: Evaluating fractional Laplacian or
  boundary element methods.  
  \item Non-matching discretizations: Integrating data between two independent
  discretization schemes that overlap in some areas. 
  \item Bulk-surface coupling: Combining data from a bulk discretization and
  a surface discretization.
 \end{itemize}

The new class enables the combination of degrees of freedom indices, shape
functions, and quadrature points from two existing \texttt{FEValuesBase}
objects. The way this combination is performed is controlled by user-provided
\texttt{DoFCouplingType} and \texttt{QuadratureCouplingType} objects, which
define how the degrees of freedom and quadrature points are combined.
